\documentclass[a4paper, 12pt]{extarticle}
\usepackage[a4paper, total={6in, 10in}]{geometry}
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{indentfirst}

\title{Value Education - 1\\
Gandhi and Pedal Power
}

\author{Sankalp S Bhat\\
2020112018
}
\begin{document}
\maketitle
\thispagestyle{empty}

\section*{About the Session}
This session portrayed the use of energy in a reckless way, the over expenditure of non renewable resources and some global icons who are pushing for more action on the fronts of conservation of resources. This meeting zeroed in on the tremendous impact that the excessive utilization of energy is having on our planet. 

Professor Pallavi Varma Patil from Azeem Premji University presented to us a series of clips shot across the world, showcasing the adversities people in poorer countries have faced, and their noble inventions that help us reduce our carbon footprint. 
      
\section*{What I liked about the session}

What I really liked about the session was the ingenuity of the people in combating resource exploitation, especially the various bicycle powered inventions such as the bike powered washing machine, dubbed the "Spin Cycle".
    
I am also in agreement with the benefits that come along with adopting bikes, namely the produced energy being used to power various other tasks that take up very less power, and the benefits of exercise that come along with bikes.

I also have great admiration for the people of Guatemala who have successfully adopted the use of bikes to generate power on a medium level scale.
     
 \section*{What I disliked about the session}
 
I disagree with the notion that bikes can be adopted to generate power on a large scale, and am not too cheerful about the effect it will have in lowering energy consumption costs.

I am also displeased about the lack of practical real world solutions pertaining to renewable energy, that we as citizens of a developing country can take to reduce our ever-increasing carbon footprint.

 \section*{Takeaways}
    
I realised that we need to take action now to generate power in a safe and renewable way, while also being cognizant of the resource needs of developing nations.

\end{document}
