\documentclass[a4paper, 12pt]{extarticle}
\usepackage[a4paper, total={6in, 10in}]{geometry}
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{indentfirst}
\pagenumbering{gobble} 

\title{Value Education - 1\\
\bf{Elon Musk - My Role Model}}

\author{Sankalp S Bhat\\
2020112018
}
\begin{document}
\maketitle
\pagestyle{plain}

A role model to me is a person with very strong characteristics and many impressive qualities, that perfectly qualifies him to be my role model. We discover such a large amount of people around us that we admire exceedingly in one way or the other. This person could be a hardworking vegetable seller or an astronaut. We must learn to identify strong traits that make a person admirable and imbibe as many good qualities as we can from them. Only then can we better ourselves.\\


To me, Elon Musk is that ideal character. An incredibly successful businessman and a unique innovator, Elon Musk has already earned a place in the annals of contemporary business history. He saw three challenges: the necessity to form a unifying, user-friendly internet for commerce (later expanded to assuring safe and reliable artificial intelligence), the requirement to manoeuvre far away from our dependency on fossil fuels, by researching clean and renewable energy with electrical vehicles and, finally, the necessity to supply a long-term solution towards the likelihood of human extinction, by exploring newer depths of space and establishing colonies where man has never been before.\\


Beyond inspirational, Musk’s leadership will be perceived as transformational, since it's a mix of idealized influence and intellectual stimulation, with a very important focus on individualized consideration, wherein the leader acts as a mentor and coach, while progressing to the wants of each of his followers. Musk has achieved a standard for transformational leadership that's now studied in business schools.\\


Throughout his journey within the business world, Musk created and has maintained a private brand of honesty and transparency. this is often why his followers and investors have cursed with him through periods of economic instability and bottom lines of income statements that resulted in red. Elon Musk thinks about the future of humanity and has an immense vision to transform humanity. He has also been consistently honest about his vision to strive towards a better future for the planet. Musk confessed that, \textit{“Most people, once they make plenty of cash don’t want to risk it. For me, it had been never about money but solving problems for the longer term of humanity.”} This honesty has attracted those that are think towards the long run, and who follow Musk’s prediction that in thirty years, the bulk of cars manufactured within the U.S. are going to be fully electric, and that by 2040, somebody's colony will already be established on Mars.

\end{document}
