\documentclass[a4paper, 12pt]{extarticle}
\usepackage[a4paper, total={6in, 10in}]{geometry}
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{indentfirst}

\title{Value Education - 1\\
Knowledge Knots - \uppercase\expandafter{\romannumeral3\relax}}

\author{Sankalp S Bhat\\
2020112018
}
\begin{document}
\maketitle
\thispagestyle{empty}

\section*{About the Session}
Being the third and final session in a three part series about general knowledge and related things, this session was about how general knowledge is getting talked about less and less by the modern generation, and how the vast depth and intrigue of the subject holds a lot of charm.

Dr. Harjinder "Laltu" Singh presented to us a series of images explaining and dissecting the various facets of perception of general knowledge, about judgement, and about making the correct decision - relating to decision making skills.
      
\section*{What I liked about the session}

What I really liked about the session was how the speaker addressed various attributes and parameters relating to decision making skills, by giving examples about financial and emotional losses incurred by people.
    
I also loved how Laltu used an example holding relevance in current society while he talked about subjects like mathematics or science, talking about Dalton's Atomic Theory and about combination of molecules and chemicals.

 \section*{What I disliked about the session}
 
While I fully agree with the speaker for the most part of the presentation, I must say that I couldn't really agree with how the speaker talked in concrete terms about decision making skills. I believe decisions can often not be reached quickly, and often times wrong decisions can lead to good learning experiences.

\section*{Takeaways}
    
I realise that I had to challenge myself constantly to improve myself, and be more definitive and trust myself more in the decisions I take, and to not regret every bad decision you take. We must also take utmost care to identify fake and polarizing news, while also staying up to date on current affairs.

\end{document}
