\documentclass[a4paper, 12pt]{extarticle}
\usepackage[a4paper, total={6in, 10in}]{geometry}
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{indentfirst}

\title{Value Education - 1\\
Nurturing Relationships -1}

\author{Sankalp S Bhat\\
2020112018
}
\begin{document}
\maketitle
\thispagestyle{empty}

\section*{About the Session}
This session was about how we perceive relationships in our day to day lives. We also talked about we look at people around us, and how our perceptions of them affect our relationships with them. Humans are a social creature, and having and maintaining relationships with the people around us is a crucial part of our daily existence.

Prof. Dipti Misra presented to us a series of images explaining and dissecting the various relationships that we hold, ranging from parents, teachers, friends, siblings etc. Another important topic up for discussion was the stability of different relationships in our lives, and how expectations from both sides of the party play an important part in determining the stability of the relationship. 
      
\section*{What I liked about the session}

What I really liked about the session was how the speaker addressed various attributes and parameters that define a relationship, and how they were related to the overall health of the relationship.
    
I also loved how Prof. Dipti used personal anecdotes to better explain to us how to manage expectations in a relationship, and also how participation is expected from both parties to manage a relationship properly.

Another aspect of the presentation that resonated with me was about boundaries, and how to set appropriate boundaries in a relationship so as to not disappoint ourselves.
     
 \section*{What I disliked about the session}
 
Something that could also have been touched upon more was how to maintain ourselves in a relationship in such a way that would benefit both parties appropriately.

I also feel that physical aspects such as how to frame your speech and how to carry yourselves could've been touched upon more
 \section*{Takeaways}
    
I realise how neglectful I have been towards introspecting on the relationships that I have been a part of, and will commit myself to play a more active role in managing my expectations appropriately henceforth.

\end{document}
